\textit{Red Oak}: Proactive Policy Generation

### 2015-05-10 draft.tex
..

From an algorithmic policy such as the one included in Fig~\ref{fig:firewall-eg}, we generate a decision tree summarizing the function's interaction with the packet and the relevant decisions that will be made for particular classes of packets. The decision tree is created by analyzing the programmers function statically and then used by our runtime system to install switch rules and update them only when necessary (i.e., in response to changes in global state). For the stateful firewall included in figure~\ref{fig:firewallcode}, the following decision tree would be generated:

@@

 For example, after having seen a packet with \lstinline|ipsrc| 10 and \lstinline|ipdst| 150, the first rules would be matched, evaluating the decision tree would add tuple $(10,150)$ to relation \lstinline|conn|, the packet would be forwarded according to the forwarding decision \lstinline|Deliver|, and the concrete rules would updated as follow:

@@

>>>>

From an algorithmic policy such as the one included in Fig~\ref{fig:firewallcode}, we generate a decision tree summarizing the function's interaction with the packet and the relevant decisions that will be made for particular classes of packets. The decision tree is created by analyzing the programmers function statically and then used by our runtime system to install switch rules and update them only when necessary (i.e., in response to changes in global state). For the stateful firewall included in figure~\ref{fig:firewallcode}, the following decision tree would be generated:

@@

  For example, a packing coming from \lstinline|ipsrc| 150 and \lstinline|ipdst| 10 would be matched by the second rule, and dropped on the switch.
Subsequently, on a packet with \lstinline|ipsrc| 10 and \lstinline|ipdst| 150, the first rules would be matched, evaluating the decision tree would add tuple $(10,150)$ to relation \lstinline|conn|, the packet would be forwarded according to the forwarding decision \lstinline|Deliver|, and the concrete rules would updated as follow:

@@

In this example, packet traveling from \lstinline|150| to \lstinline|10| would be matched by the second rule on the switch and delivered, while packets from \lstinline|150| to other internal hosts or from other external host to any internal hosts would be dropped.
